Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-12-15 doc/article.tex
simplify the conditional likelihood equation

Assembling this together, the likelihood is
\begin{equation}
\mathcal{L}(data|\mathcal{S}, model) = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata\,
\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)
}
\end{equation}
where the normalizing factor is included explicitly as it has 
parameter dependence and must not be neglected in calculations.

>>>>

Assembling this together, the likelihood is
\begin{align}
\mathcal{L}(data|\mathcal{S}, model) & = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata'\,
\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o', b_k)p(data'| model)
}\\
& = \frac{p(data| model)}{\int ddata'\,
\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o', b_k)p(data'| model)
}
\end{align}
where the normalizing factor is included explicitly as it has 
parameter dependence and must not be neglected in calculations.
